\Title

### 2020-02-17 manuscript/manuscript.tex
Rename block-median to block averaged

We propose a new source distribution that could simultaneously solve the
problems of the preceding ones: the \emph{block-median sources}.
It consist in dividing the region in blocks of equal size, computing the median
location of the observation points that fall inside each block, and putting one
point source bellow this block-median coordinate.
It creates one point source beneath each populated block, solving the problem
of the \emph{grid sources} layout, but also reducing the number of point
sources in comparison with the \emph{source beneath data} layout.

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/block-median-sources-schematics.pdf}
    \caption{
        Block-median sources. Given a set of observation points (a) we divide
        the survey region on blocks of equal size (b) and compute the median
        location of the observation points that fall inside each block.
        A source point is located beneath each block-median coordinate (c).
        The number of point sources could be less or equal to the number of
        observation points.
        No source is located beneath unpopulated blocks.
    }
    \label{fig:depth-types}
\end{figure*}

@@

One possible solution is to locate each source bellow its corresponding
observation point or block-median point at a constant \emph{relative depth}
from it.
The sources won't be all at the same depth, but they will all be at the same
distance from their corresponding observation point (or block-median point).
It worth mention that this approach could not be applied to \emph{grid
sources}.

@@

\noindent where \emph{data point height} is the elevation of the corresponding
observation (or block-median) point to the source, \emph{depth factor} and
\emph{relative depth} are parameters and \emph{mean distance} is the mean
distance to the $k$ nearest source neighbours.

@@

\begin{table*}
\begin{minipage}{80mm}
    \caption{
        Source distributions as combinations of source layouts and depth
        strategies.
    }
    \label{tab:source-distributions}
    \begin{tabular}{lccc}
        & Source bellow data & Block-median sources & Grid sources \\ \hline
        Constant depth          & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
        Relative depth          & $\checkmark$ & $\checkmark$ & $\times$     \\
        Variable relative depth & $\checkmark$ & $\checkmark$ & $\times$     \\
    \end{tabular}
\end{minipage}
\end{table*}

>>>>

We propose a new source distribution that could simultaneously solve the
problems of the preceding ones: the \emph{block averaged sources}.
It consist in dividing the region in blocks of equal size, computing the median
location of the observation points that fall inside each block, and putting one
point source bellow this block averaged coordinate
(fig.~\ref{fig:block-median-sources}).
It creates one source beneath each populated block, solving the problem
of the \emph{grid sources} layout, but also reducing the number of point
sources in comparison with the \emph{source beneath data} layout.

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/block-median-sources-schematics.pdf}
    \caption{
        Block averaged sources. Given a set of observation points (a) we divide
        the survey region on blocks of equal size (b) and compute the median
        location of the observation points that fall inside each block.
        A source point is located beneath each block averaged coordinate (c).
        The number of point sources could be less or equal to the number of
        observation points.
        No source is located beneath unpopulated blocks.
    }
    \label{fig:block-median-sources}
\end{figure*}

@@

One possible solution is to locate each source bellow its corresponding
observation point or block averaged point at a constant \emph{relative depth}
from it.
The sources won't be all at the same depth, but they will all be at the same
distance from their corresponding observation point (or block averaged point).
It worth mention that this approach could not be applied to \emph{grid
sources}.

@@

\noindent where \emph{data point height} is the elevation of the corresponding
observation (or block averaged) point to the source, \emph{depth factor} and
\emph{relative depth} are parameters and \emph{mean distance} is the mean
distance to the $k$ nearest source neighbours.

@@

\begin{table*}
\begin{minipage}{80mm}
    \caption{
        Source distributions as combinations of source layouts and depth
        strategies.
    }
    \label{tab:source-distributions}
    \begin{tabular}{lccc}
        & Source bellow data & Block averaged sources & Grid sources \\ \hline
        Constant depth          & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
        Relative depth          & $\checkmark$ & $\checkmark$ & $\times$     \\
        Variable relative depth & $\checkmark$ & $\checkmark$ & $\times$     \\
    \end{tabular}
\end{minipage}
\end{table*}
